Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2024-11-29 paper/main.tex
Updates figure 1

\caption{Markov Equivalence Class (MEC) learnt for Adult Income Dataset using (a) PC algorithm, (b) Hill-Climb Search with BIC score, (c) }
\label{fig:intro}
\end{figure}

>>>>

\caption{Markov Equivalence Class (MEC) learnt for Adult Income Dataset using (a) PC algorithm, (b) Hill-Climb Search with BIC score, (c) PC algorithm with MXM test}
\label{fig:intro}
\end{figure}
